\section{Lessons Learnt}
Our team came across different challenges and obstacles from the beginning of the project. Our team's learning during this project is twofold.  While in terms of technicality, our learning outcome was not much, in terms of project management our learning was far more significant. The points mentioned below are what the team has learned throughout this journey.
\subsection{Managerial Learning}
\begin{itemize}
    \item It is very important for the team to start the project with a project that is conceptualized properly. The team relocated to this project on week 4 after realizing that the previous project idea was not completely fleshed-out. Since the unit duration is too short the team thought it would be better if we could work on something that is properly conceptualized and the ideas of deliverables are clear to the sponsors. The team communicated with the course coordinators and sponsor and took the necessary steps to work on this project which the team considers a good negotiation skill.
    \item As the principal work with the current sponsor started after week 4 the team had to go through really intense cooperation to catch up with the progress with other groups.
    \item The team had to work on strict deadlines which made other members undertake the responsibilities that were assigned to someone. We consider this as a healthy work ethic.
\end{itemize}
\subsection{Technical Learning}
\begin{itemize}
    \item To work parallelly the team learned to use various collaborative tools like \verb|google colab|, \verb|git|, \verb|github|, etc. 
    \item Gaining access to a workable dataset was extremely limited for this project since it held government data. So the team had to learn the problems and prospects of working with the data that were sensitive.
    \item Our team had to work on a dataset that held aggregated data, which made everything challenging. Each member had to extract and compile the information they were interested in and came up with new datasets from the extracted datasets so that they provided information as robust as the datasets that are not aggregated.
\end{itemize}