\section{Recommendations to the Sponsor}
In our opinion, our sponsor was extremely helpful and communicative. Our sponsor gave us the freedom of choice about what analysis we come up with, what can be the outcome and what are the deliverables. The sponsor also helped the team communicate with the dataset owners from the government agencies which as AIHW. She suggested that should not wait for 2 months for AIHW to give us a fraction of the atomic dataset they own and start working on the aggregated dataset that is publicly accessible. However, the team understands that the analysis would have been more specific if there was access to a more workable dataset that is not aggregated which would allow the team to make better analyses and models for forecasting.

The project sponsor was very supportive and communicated effectively throughout the process. The sponsor provided the team with the autonomy to determine the scope of analysis, anticipated outcomes, and corresponding deliverables. Furthermore, the sponsor facilitated communication between the research team and data owners at the Australian Institute of Health and Welfare (AIHW). Specifically, the sponsor advised the team to proceed with analyzing the publicly accessible aggregated dataset instead of waiting for the AIHW to provide a portion of the atomic dataset, which could take up to two months. Nonetheless, the team acknowledges that accessing a more detailed and comprehensive dataset could have enabled more refined analyses and more accurate forecasting models.