\section{Risks Mitigated}
% Risk analysis should include what mitigation IS being taken, by who, and what the resultant (after risk) is. I suggest you use a table with a rating of each risk. These risks are too general for a project report of this nature.
Following are the risks the team predicted and faced during different lifecycles of the project and explained how they were mitigated.

\subsection{Data privacy and security risks} Given the sensitive nature of the data, it was important to ensure that appropriate measures were taken to protect data privacy and security. The data the team used was collected by principally Australian Bureau of Statistics and then aggregated by AIHW. Both of these organizations maintain strict vulnerability and disclosure policies\cite{vulPol} which made sure that the data has abstraction (such as aggregating data) from giving away personal information.

\subsection{Data quality risks} Poor quality data can compromise the accuracy and reliability of the analysis. The datasets that the team had to work on had unorganized data in some of them. Each analysis was done after extracting and compiling the data that was relevant to our objective.

\subsection{Ethical risks} It was important to ensure that the project adheres to ethical principles and guidelines. Since we did not have to collect any data that belonged to an individual or a specific group, the team feels that the analysis is done with proper ethical standards.

\subsection{Project management risks} Effective project management is crucial for ensuring that the project is completed on time and within budget. The team worked on track of previously developed project plans  and followed milestones and timelines. The tasks were delegated among the members appropriately. Also, effective communication and collaboration among team members were ensured.

\subsection{Analysis and interpretation risks} The analysis and interpretation of the data can be influenced by biases, assumptions, and other subjective factors. To mitigate these problems, appropriate statistical methods, conducting sensitivity analyses to assess the impact of different assumptions were performed for each analysis ensuring that the analysis and interpretation are well-documented and transparent.
