\section{Used Resources}
\subsection{Hardware Resources}
 No external hardware was required. The use of each individual's machine had been decided for data analysis, visualization, forecasting, etc. In the case of dealing with robust data, the remote computers from the university laboratory had been considered, which had capable Nvidia GPUs for the tasks displayed in the report.
\subsection{Software Resources}
\begin{itemize}
    \item Rstudio
    \item Pycharm
    \item Python 3.8
    \item Microsoft Excel
    \item Git for version controlling and contribution management
    \item Discord for internal team communication
\end{itemize}

\section{Project Resources}
Requirements for this project include
\subsection{Data Sources}
\begin{itemize}
    \item Since this project aims to work alongside AIHW the team has considered AIHW as their primary data source. Although, the data available on the AIHW website are summary or aggregated data and it does not include individual records. Their 3 primary data sources which are National Perinatal Data Collection, National Perinatal Mortality Data Collection \& National Maternal Mortality Data Collection’s data can be accessed by making a request with table specifications to the data provider.
    \item Our team wants to use the Australian Bureau of Statistics data on birth as a secondary dataset. These datasets have records from 1991-2021 of birth data. It includes the data describing parent’s birthplace, age, ethnicity if they are aboriginal, the birthrate of the area, etc which can play vital role in this project’s analysis.
\end{itemize}
\subsection{Budget}
The 3 different data sources do not mention any price per record but from the team’s understanding, it is assumed that the allocated AUD300 should cover the data requested from the sources. Since no new hardware is required for the completion of this project, no budget is being considered for purchasing or gaining access to new hardware.
